
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Topic Models

## Loading packages; installing package "seededlda"
```{r}

install.packages("seededlda")

library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(seededlda)
library(ggplot2)
```

## Getting data ready
You know the drill: Import data, create corpus, tokenize and remove non-text, create dfm, remove stopwords, wordstem. I recommend working with the eurydice data at this point. You could also work with the presidential election debate, but the eurydice corpus is larger and therefore well suited for machine learning.

```{r}

```


## LDA Topic Modelling (Unsupervised)
Now you can run an unsupervised LDA topic model. 

1. Use the textmodel_lda() command. In the brackets you should define the dfm this model should learn from and the anmount of topic (k=x). Both specifications are separated with a comma. Before you run it, make sure to assign the model to an object in the enviornment (x <- textmodel_lda())
2. What terms are associated with each topic? use the command terms(x,20) to get the top 20 terms for each topic. Try to give headlines to the topics. Then interpret the results. What are the advantages / disatvantages of using unsupervised topic modelling?

```{r}
# run the model. This will take time.


# what are the terms associated with each topic?


```
3. Lets get a list of the prevalent topics of the first 20 documents(texts) using the command 'head(topics(x), 20)'. Replace x with the name you gave your topic model.

```{r}
# get prevalent topics of first 20 documents (texts)


```

4. To compare the topic frequency we first assign the topic as a new dicument-level variable (docvar). Use the following command 'x$topic <- topics(x)' where the first x is your dfm and the second x is your topic model.

5. To compare the prevalence of topics, use the table() function. The command is table(x$topic) where x is your dfm to which you have assigend 'topic' as a new docvar. The table will list the topics and tell you in how many documents they are prevalent.

```{r}
# assign topic as a new document-level variable


# cross-table of the topic frequency


```


## Seeded Topic Model (Supervised)
In  seeded LDA, you can predefine topics using a dictionary of “seed words". Before running the model you need to define a dictionary using the dictionary() command you learned in the last script. Command: X <- dictionary(list(x=c("x"), x=c("x"))). *Important*: Make sure to define at least two topics, if not more.


1. Define a dictionary with at least two topics (better more topics).

```{r}
# Define a dictionary


```

You can run the seeded lda topic model (slda) using the textmodel_seededlda() command. This will take some time. The command is as follows: x <- textmodel_seededlda(x,dictionary = x). The first x refers to the name you give your slda model, the second x refers to your dfm and the third x refers to the name of your dictionary that will provide the seed words.

2. Run the seeded lda topic model using the textmodel_seededlda() command.

3. Inspect the first 20 terms associated with each topic using the command terms(x, 20). X stands for the name of your model.

```{r}


```

You can see which topics are prevalent in the different documents using the topics() function.

4. Check which topics are prevalent in the first 20 documents using the topics() function. The command is topics(x). You can also use the 'head' command to only get the first 20. The command would be head(topics(x), 20).

```{r}



```


5. Assign topic as a new document-level variable (docvar) in your dfm. 
The command is 'x$topic <- topics(x)'. The first x represents your dfm. The second x represents your topic model model.

Now you can get a cross-table of the topic frequencies to see how prevalent which topic is in your corpus. Use the 'table(x$topic)' command. Here x is your dfm.

```{r}


```

You can attach your topics as a new variable to your data frame (the data before you make it a corpus). 

1. Transform the topics to be a data frame using the 'topics <- as.data.frame(topics(x))' command in which x is your topic model. 
2. Attach topics to original data frame using the cbind function. x <- cbind(x,topics)

```{r}


```


## Plot

Now you can plot your findings. However, you will notice the eurydice data is not good for 'simple' plots. This plot is just meant to inform your own analysis below, where you can draw on better fit between data and dictionary.

There are many ways to plot topics. I keep this plot as a simple as possible, but if you are interested in visualization, we can include a session on visualization on the last day of the seminar.

```{r}

ggplot(replace, aes(x = `topics(replace)`, y = country, colour = `topics(replace)`)) + geom_point() + 
  labs(x = "Topic", y = "Country") +
  ggtitle("Distribution of topics over countries")

```


## Exercise:
Apply topic modelling to one of the other available data sets. I recommend the UN General Assembly Corpus. Choose the type of topic modelling you want to apply. Think about what question you can answer with topic modelling.

```{r}



```
